---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# acdocudat

<!-- badges: start -->
<!-- badges: end -->

The goal of acdocudat is to help the user create a data dictionary/codebook for a user selected R dataset along with some summary statistics to help to get an initial sense of data completeness, possible outliers, and more. The package will provide functions that can be used to form different sections of the codebook, put a codebook table together, and be output to a PDF. The package will work with all different types of datasets in order to be useful within a data management setting.

## Installation

You can install the released version of acdocudat from github by running the following code:

``` r
install_github("alliecarter/581FinalProjectCarter")
```
Then, simply library(acdocudat).

## Data: mtcars

To explore the functions in this package we will use the dataset mtcars. This datasets contains fuel consumption and design variables for 32 cars and is documented in ?mtcars.

## Variable Names/Types

Oftentimes, we are given datasets to clean, summarize, or a number of other tasks. The following examples are useful to help interpret variable meanings and communicate them cleanly to an outside user or collaborator.

```{r example}
library(acdocudat)
## See what types of variables are in our dataset
varinfo(mtcars)
```

## Summary Statistics

Now we want to get a sense of how much data is missing, how many observations we have, and the ranges of data for each numeric variable
```{r}
NFun(mtcars)
```

## Variable Information Dataframe

Perhaps we may want to run everything together and get a nice table summarizing the variables available in this dataset.
```{r}
Ncomb(mtcars)
```

## Formatted Table of Codebook Information
The tablfun function will give you a nice formatted table of your variables summarized with all the information collected in Ncomb. We have the following code:

tablfun(.data, headcolor = "white", bodycolor = "white", bodftcolor = "black", topftcolor = "black")

With the following arguments:
.data	(The name of the dataset to summarize.)

headcolor	(The background color of the header of the table.)

bodycolor	(The background color of the body of the table.)

bodftcolor	(The font color of the header of the table.)

topftcolor	(The font color of the body of the table.)


## Read Table/Codebook out to PDF File

Depending on if we will be presenting/collaborating, we may want to have a cleaner, formatted output of variable information to share with others.

If we are sharing, we can output to a pdf with a center tabled of all available summarized information.
```{r}
pdfout(mtcars, "CarsCodebook2020")
```

## Variable Summaries Interactive Shiny Gadget

Within the R session it is often helpful to be able to isolate variables one by one.
```{r}
ShinyTable(mtcars)
```




